---
title: "R Notebook"
output: html_notebook
---

The maps of Middle Earth have fascinated me ever since I got introduced to the *Lord of the Rings*, ages ago when I was a teenager.

Couple of days back, I found [this fascinating article](http://www.r-chart.com/2016/10/map-of-middle-earth-map-above-was.html) on creating map of the middle earth. 

This intrigued me and this code is my attempt to follow along the code that's available in that article.

I've made use of `R Notebooks` to run this.

To run the code, we need the following packages. If they aren't available, please install them

`ggplot2`  
`ggmap`  
`maptools`  
`rgeos`


```{r}
#Load the packages
library(ggplot2)
library(ggmap)
library(maptools)
```

`ggmap` package has a **fortify()** function to read and plot shapefiles.

Read the data using `maptools`

```{r}
coastline = readShapeSpatial('../Coastline2.shp')
forests = readShapeSpatial('../Forests.shp')
lakes = readShapeSpatial('../Lakes2.shp')
rivers = readShapeSpatial('../Rivers19.shp')
contours = readShapeSpatial('../Contours_18.shp')
```

The following code renders the map

```{r}
ggplot() +
 geom_polygon(data = fortify(contours), 
              aes(x = long, y = lat, group = group),
              color = '#f0f0f0', fill='#f0f0f0', size = .2) +
 geom_path(data = fortify(coastline), 
           aes(x = long, y = lat, group = group),
           color = 'black', size = .2) +
 geom_polygon(data = fortify(forests), 
          aes(x = long, y = lat, group = group),
          color = '#31a354', fill='#31a354', size = .2) +
 geom_polygon(data = fortify(lakes), 
            aes(x = long, y = lat, group = group),
            color = '#a6bddb', fill='#a6bddb', size = .2) +
 geom_path(data = fortify(rivers), 
            aes(x = long, y = lat, group = group),
            color = '#a6bddb', size = .2) + 
 ggtitle('Middle Earth') + 
 ylab('') + 
 xlab('Shapefiles: https://github.com/jvangeld/ME-GIS')
```


